Evaluating Informative Hypotheses with Equality and Inequality Constraints: A Tutorial Using the Bayes Factor via the Encompassing Prior Approach

### 2022-10-15 Documents/Bookdown/01-case-study.Rmd
add review supplemental materials with link to preprint

For more information regarding Attachment theory and the formalization of theoretical perspectives regarding the role of mother attachment and father attachment on children's socio-emotional development, see the main article [TODO: add link article].

>>>>

For more information regarding Attachment theory and the formalization of theoretical perspectives regarding the role of mother attachment and father attachment on children's socio-emotional development, see the main article available at https://psyarxiv.com/6kc5u.

### 2022-10-15 Documents/Bookdown/05-ext-BF.Rmd
add review supplemental materials with link to preprint

To properly evaluate hypotheses with information regarding the expected direction of the effects, we use the Bayes factor with the encompassing prior approach. See the main article for a detailed introduction to this approach [TODO: add link article].

@@

For each informative hypothesis, we obtain a hypothesis matrix that translates equality and inequality constraints according to the encompassing model parametrization. Formalization of informative hypotheses and the procedure to derive hypothesis matrices are described in the main paper ([TODO: add link]).

@@

$$
\pi_{adj}(\beta) \sim \mathcal{N}(0, \Sigma_{\beta}) = \mathcal{N}(0, R\Sigma_{\theta}R^T).
$$
Note that we set the mean vector to zero. The posterior is given by the same transformation
$$
Pr(\beta|Y) \sim \mathcal{N}(\hat{\beta}, \hat{\Sigma}_{\beta}) = \mathcal{N}(R\hat{\theta}-r, R\hat{\Sigma}_{\theta}R^T).
$$
See the main article for more details [TODO: add link].

@@

Before computing the Bayes factor, note that we have a set of comparable hypotheses as it exists a common solution to the set of linear equations obtained by setting all hypothesis constraints equal to zero. The solution is the trivial solution of simply considering all parameters equal to zero. Finally, we do not need to standardize our parameters as they represent mean groups’ differences. See the main article for a detailed explanation [TODO: add link article].

@@

To compute the Bayes factor we evaluate marginal densities and conditional probabilities as described in detail in the main article [TODO: add link article]. Bayes factor and posterior probability of each hypothesis are reported in Table~\@ref(tab:table-bf-results-ext).

@@

To interpret these patterns, remember that order constraints are insensitive to the distribution specification as long as the distribution is symmetric and centred on the constraint focal point. On the contrary, equality constraints are highly affected by the prior definition (see the main article for more details [TODO: add link article]).

>>>>

To properly evaluate hypotheses with information regarding the expected direction of the effects, we use the Bayes factor with the encompassing prior approach. See the main article for a detailed introduction to this approach (https://psyarxiv.com/6kc5u).

@@

For each informative hypothesis, we obtain a hypothesis matrix that translates equality and inequality constraints according to the encompassing model parametrization. Formalization of informative hypotheses and the procedure to derive hypothesis matrices are described in the main paper (https://psyarxiv.com/6kc5u).

@@

$$
\pi_{adj}(\beta) \sim \mathcal{N}(0, \Sigma_{\beta}) = \mathcal{N}(0, R\Sigma_{\theta}R^T).
$$
Note that we set the mean vector to zero. The posterior is given by the same transformation
$$
Pr(\beta|Y) \sim \mathcal{N}(\hat{\beta}, \hat{\Sigma}_{\beta}) = \mathcal{N}(R\hat{\theta}-r, R\hat{\Sigma}_{\theta}R^T).
$$
For more details, see the main article available at https://psyarxiv.com/6kc5u.

@@

Before computing the Bayes factor, note that we have a set of comparable hypotheses as it exists a common solution to the set of linear equations obtained by setting all hypothesis constraints equal to zero. The solution is the trivial solution of simply considering all parameters equal to zero. Finally, we do not need to standardize our parameters as they represent mean groups’ differences. For a detailed explanation, see the main article available at https://psyarxiv.com/6kc5u.

@@

To compute the Bayes factor we evaluate marginal densities and conditional probabilities as described in detail in the main article (https://psyarxiv.com/6kc5u). Bayes factor and posterior probability of each hypothesis are reported in Table~\@ref(tab:table-bf-results-ext).

@@

To interpret these patterns, remember that order constraints are insensitive to the distribution specification as long as the distribution is symmetric and centred on the constraint focal point. On the contrary, equality constraints are highly affected by the prior definition (for more details, see the main article available at https://psyarxiv.com/6kc5u).

### 2022-10-15 Documents/Bookdown/index.Rmd
add review supplemental materials with link to preprint

This is the Supplemental Material of the article “*Evaluating informative hypotheses with equality and inequality constraints: A tutorial using the Bayes factor via the encompassing prior approach*” [TODO: add cit]. The paper aims to provide a clear and detailed description of the Bayes Factor with the encompassing prior approach considering an applied example.

@@

In the supplemental material, we provide the complete statistical analyses of the case study regarding attachment. For more information regarding the Bayes factor with encompassing prior approach or the formalization of theoretical perspectives regarding the role of mother attachment and father attachment on children socio-emotional development, see the main article [TODO: add link article]. The supplemental material is structured into three parts:

>>>>

This is the Supplemental Material of the article “*Evaluating informative hypotheses with equality and inequality constraints: A tutorial using the Bayes factor via the encompassing prior approach*” available at https://psyarxiv.com/6kc5u. The paper aims to provide a clear and detailed description of the Bayes Factor with the encompassing prior approach considering an applied example.

@@

In the supplemental material, we provide the complete statistical analyses of the case study regarding attachment. For more information regarding the Bayes factor with encompassing prior approach or the formalization of theoretical perspectives regarding the role of mother attachment and father attachment on children socio-emotional development, see the main article available at https://psyarxiv.com/6kc5u. The supplemental material is structured into three parts:

### 2022-10-15 docs/attachment-bayes-factor.tex
add review supplemental materials with link to preprint

@@

\title{Evaluating Informative Hypotheses with Equality and Inequality Constraints: A Tutorial Using the Bayes Factor via the Encompassing Prior Approach}
\usepackage{etoolbox}
\makeatletter
\providecommand{\subtitle}[1]{% add subtitle to \maketitle
  \apptocmd{\@title}{\par {\large #1 \par}}{}{}
}
\makeatother
\subtitle{Supplemental Material}
\author{\href{https://claudiozandonella.netlify.app/}{Claudio Zandonella Callegher}, Tatiana Marci, Pietro De Carli, and Gianmarco Altoè}
\date{2022-09-25}

@@

This is the Supplemental Material of the article ``\emph{Evaluating informative hypotheses with equality and inequality constraints: A tutorial using the Bayes factor via the encompassing prior approach}'' {[}TODO: add cit{]}. The paper aims to provide a clear and detailed description of the Bayes Factor with the encompassing prior approach considering an applied example.

@@

In the supplemental material, we provide the complete statistical analyses of the case study regarding attachment. For more information regarding the Bayes factor with encompassing prior approach or the formalization of theoretical perspectives regarding the role of mother attachment and father attachment on children socio-emotional development, see the main article {[}TODO: add link article{]}. The supplemental material is structured into three parts:

@@

For more information regarding Attachment theory and the formalization of theoretical perspectives regarding the role of mother attachment and father attachment on children's socio-emotional development, see the main article {[}TODO: add link article{]}.

@@

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{emmeans}\SpecialCharTok{::}\FunctionTok{contrast}\NormalTok{(emmeans}\SpecialCharTok{::}\FunctionTok{emmeans}\NormalTok{(fit\_ext\_zinb, }\AttributeTok{specs =} \SpecialCharTok{\textasciitilde{}}\NormalTok{ mother ),}
                  \StringTok{"pairwise"}\NormalTok{, }\AttributeTok{adjust =} \StringTok{"mvt"}\NormalTok{)}
\DocumentationTok{\#\# }\AlertTok{NOTE}\DocumentationTok{: Results may be misleading due to involvement in interactions}
\DocumentationTok{\#\#  contrast           estimate    SE  df t.ratio p.value}
\DocumentationTok{\#\#  Secure {-} Anxious    {-}0.2856 0.140 825  {-}2.034  0.1719}
\DocumentationTok{\#\#  Secure {-} Avoidant   {-}0.3080 0.162 825  {-}1.902  0.2228}
\DocumentationTok{\#\#  Secure {-} Fearful    {-}0.5617 0.178 825  {-}3.149  0.0089}
\DocumentationTok{\#\#  Anxious {-} Avoidant  {-}0.0224 0.124 825  {-}0.181  0.9978}
\DocumentationTok{\#\#  Anxious {-} Fearful   {-}0.2761 0.146 825  {-}1.885  0.2300}
\DocumentationTok{\#\#  Avoidant {-} Fearful  {-}0.2537 0.167 825  {-}1.522  0.4179}
\DocumentationTok{\#\# }
\DocumentationTok{\#\# Results are averaged over the levels of: gender, father }
\DocumentationTok{\#\# Results are given on the log (not the response) scale. }
\DocumentationTok{\#\# P value adjustment: mvt method for 6 tests}
\end{Highlighting}
\end{Shaded}

@@

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{emmeans}\SpecialCharTok{::}\FunctionTok{contrast}\NormalTok{(emmeans}\SpecialCharTok{::}\FunctionTok{emmeans}\NormalTok{(fit\_ext\_mother, }\AttributeTok{specs =} \SpecialCharTok{\textasciitilde{}}\NormalTok{ mother ),}
                  \StringTok{"pairwise"}\NormalTok{, }\AttributeTok{adjust =} \StringTok{"mvt"}\NormalTok{)}
\DocumentationTok{\#\#  contrast           estimate     SE  df t.ratio p.value}
\DocumentationTok{\#\#  Secure {-} Anxious    {-}0.2432 0.1034 837  {-}2.353  0.0859}
\DocumentationTok{\#\#  Secure {-} Avoidant   {-}0.3080 0.1091 837  {-}2.823  0.0243}
\DocumentationTok{\#\#  Secure {-} Fearful    {-}0.5268 0.1313 837  {-}4.011  0.0004}
\DocumentationTok{\#\#  Anxious {-} Avoidant  {-}0.0648 0.0981 837  {-}0.661  0.9107}
\DocumentationTok{\#\#  Anxious {-} Fearful   {-}0.2836 0.1216 837  {-}2.333  0.0903}
\DocumentationTok{\#\#  Avoidant {-} Fearful  {-}0.2188 0.1276 837  {-}1.714  0.3135}
\DocumentationTok{\#\# }
\DocumentationTok{\#\# Results are averaged over the levels of: gender }
\DocumentationTok{\#\# Results are given on the log (not the response) scale. }
\DocumentationTok{\#\# P value adjustment: mvt method for 6 tests}
\end{Highlighting}
\end{Shaded}

@@

To properly evaluate hypotheses with information regarding the expected direction of the effects, we use the Bayes factor with the encompassing prior approach. See the main article for a detailed introduction to this approach {[}TODO: add link article{]}.

@@

For each informative hypothesis, we obtain a hypothesis matrix that translates equality and inequality constraints according to the encompassing model parametrization. Formalization of informative hypotheses and the procedure to derive hypothesis matrices are described in the main paper ({[}TODO: add link{]}).

@@

\[
\pi_{adj}(\beta) \sim \mathcal{N}(0, \Sigma_{\beta}) = \mathcal{N}(0, R\Sigma_{\theta}R^T).
\]
Note that we set the mean vector to zero. The posterior is given by the same transformation
\[
Pr(\beta|Y) \sim \mathcal{N}(\hat{\beta}, \hat{\Sigma}_{\beta}) = \mathcal{N}(R\hat{\theta}-r, R\hat{\Sigma}_{\theta}R^T).
\]
See the main article for more details {[}TODO: add link{]}.

@@

Before computing the Bayes factor, note that we have a set of comparable hypotheses as it exists a common solution to the set of linear equations obtained by setting all hypothesis constraints equal to zero. The solution is the trivial solution of simply considering all parameters equal to zero. Finally, we do not need to standardize our parameters as they represent mean groups' differences. See the main article for a detailed explanation {[}TODO: add link article{]}.

@@

To compute the Bayes factor we evaluate marginal densities and conditional probabilities as described in detail in the main article {[}TODO: add link article{]}. Bayes factor and posterior probability of each hypothesis are reported in Table\textasciitilde\ref{tab:table-bf-results-ext}.

@@

To interpret these patterns, remember that order constraints are insensitive to the distribution specification as long as the distribution is symmetric and centred on the constraint focal point. On the contrary, equality constraints are highly affected by the prior definition (see the main article for more details {[}TODO: add link article{]}).

@@

\begin{verbatim}
## Warning: Argument 'nsamples' is deprecated. Please use argument 'ndraws' instead.
\end{verbatim}

@@

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{emmeans}\SpecialCharTok{::}\FunctionTok{contrast}\NormalTok{(emmeans}\SpecialCharTok{::}\FunctionTok{emmeans}\NormalTok{(fit\_int\_mother, }\AttributeTok{specs =} \SpecialCharTok{\textasciitilde{}}\NormalTok{ mother ),}
                  \StringTok{"pairwise"}\NormalTok{, }\AttributeTok{adjust =} \StringTok{"mvt"}\NormalTok{)}
\DocumentationTok{\#\#  contrast           estimate     SE  df t.ratio p.value}
\DocumentationTok{\#\#  Secure {-} Anxious     {-}0.285 0.0892 837  {-}3.197  0.0079}
\DocumentationTok{\#\#  Secure {-} Avoidant    {-}0.120 0.0946 837  {-}1.266  0.5809}
\DocumentationTok{\#\#  Secure {-} Fearful     {-}0.469 0.1168 837  {-}4.011  0.0003}
\DocumentationTok{\#\#  Anxious {-} Avoidant    0.165 0.0869 837   1.903  0.2243}
\DocumentationTok{\#\#  Anxious {-} Fearful    {-}0.183 0.1096 837  {-}1.673  0.3346}
\DocumentationTok{\#\#  Avoidant {-} Fearful   {-}0.349 0.1167 837  {-}2.989  0.0149}
\DocumentationTok{\#\# }
\DocumentationTok{\#\# Results are averaged over the levels of: gender }
\DocumentationTok{\#\# Results are given on the log (not the response) scale. }
\DocumentationTok{\#\# P value adjustment: mvt method for 6 tests}
\end{Highlighting}
\end{Shaded}

>>>>

%----    layout    ----%

% change margins
\usepackage[outer = 105pt, inner = 85pt]{geometry}
\usepackage{afterpage}
\voffset 5pt
\headsep 29pt
\footskip 35pt
\textheight 590pt
\usepackage{layout}% http://ctan.org/pkg/layouts

% caption
\usepackage[labelfont=bf]{caption}

@@

\title{Evaluating Informative Hypotheses with Equality and Inequality Constraints: A Tutorial Using the Bayes Factor via the Encompassing Prior Approach}
\usepackage{etoolbox}
\makeatletter
\providecommand{\subtitle}[1]{% add subtitle to \maketitle
  \apptocmd{\@title}{\par {\large #1 \par}}{}{}
}
\makeatother
\subtitle{Supplemental Material}
\author{\href{https://claudiozandonella.netlify.app/}{Claudio Zandonella Callegher}, Tatiana Marci, Pietro De Carli, and Gianmarco Altoè}
\date{2022-10-15}

@@

This is the Supplemental Material of the article ``\emph{Evaluating informative hypotheses with equality and inequality constraints: A tutorial using the Bayes factor via the encompassing prior approach}'' available at \url{https://psyarxiv.com/6kc5u}. The paper aims to provide a clear and detailed description of the Bayes Factor with the encompassing prior approach considering an applied example.

@@

In the supplemental material, we provide the complete statistical analyses of the case study regarding attachment. For more information regarding the Bayes factor with encompassing prior approach or the formalization of theoretical perspectives regarding the role of mother attachment and father attachment on children socio-emotional development, see the main article available at \url{https://psyarxiv.com/6kc5u}. The supplemental material is structured into three parts:

@@

For more information regarding Attachment theory and the formalization of theoretical perspectives regarding the role of mother attachment and father attachment on children's socio-emotional development, see the main article available at \url{https://psyarxiv.com/6kc5u}.

@@

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{emmeans}\SpecialCharTok{::}\FunctionTok{contrast}\NormalTok{(emmeans}\SpecialCharTok{::}\FunctionTok{emmeans}\NormalTok{(fit\_ext\_zinb, }\AttributeTok{specs =} \SpecialCharTok{\textasciitilde{}}\NormalTok{ mother ),}
                  \StringTok{"pairwise"}\NormalTok{, }\AttributeTok{adjust =} \StringTok{"mvt"}\NormalTok{)}
\DocumentationTok{\#\# }\AlertTok{NOTE}\DocumentationTok{: Results may be misleading due to involvement in interactions}
\DocumentationTok{\#\#  contrast           estimate    SE  df t.ratio p.value}
\DocumentationTok{\#\#  Secure {-} Anxious    {-}0.2856 0.140 825  {-}2.034  0.1720}
\DocumentationTok{\#\#  Secure {-} Avoidant   {-}0.3080 0.162 825  {-}1.902  0.2228}
\DocumentationTok{\#\#  Secure {-} Fearful    {-}0.5617 0.178 825  {-}3.149  0.0089}
\DocumentationTok{\#\#  Anxious {-} Avoidant  {-}0.0224 0.124 825  {-}0.181  0.9978}
\DocumentationTok{\#\#  Anxious {-} Fearful   {-}0.2761 0.146 825  {-}1.885  0.2299}
\DocumentationTok{\#\#  Avoidant {-} Fearful  {-}0.2537 0.167 825  {-}1.522  0.4180}
\DocumentationTok{\#\# }
\DocumentationTok{\#\# Results are averaged over the levels of: gender, father }
\DocumentationTok{\#\# Results are given on the log (not the response) scale. }
\DocumentationTok{\#\# P value adjustment: mvt method for 6 tests}
\end{Highlighting}
\end{Shaded}

@@

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{emmeans}\SpecialCharTok{::}\FunctionTok{contrast}\NormalTok{(emmeans}\SpecialCharTok{::}\FunctionTok{emmeans}\NormalTok{(fit\_ext\_mother, }\AttributeTok{specs =} \SpecialCharTok{\textasciitilde{}}\NormalTok{ mother ),}
                  \StringTok{"pairwise"}\NormalTok{, }\AttributeTok{adjust =} \StringTok{"mvt"}\NormalTok{)}
\DocumentationTok{\#\#  contrast           estimate     SE  df t.ratio p.value}
\DocumentationTok{\#\#  Secure {-} Anxious    {-}0.2432 0.1034 837  {-}2.353  0.0858}
\DocumentationTok{\#\#  Secure {-} Avoidant   {-}0.3080 0.1091 837  {-}2.823  0.0248}
\DocumentationTok{\#\#  Secure {-} Fearful    {-}0.5268 0.1313 837  {-}4.011  0.0003}
\DocumentationTok{\#\#  Anxious {-} Avoidant  {-}0.0648 0.0981 837  {-}0.661  0.9107}
\DocumentationTok{\#\#  Anxious {-} Fearful   {-}0.2836 0.1216 837  {-}2.333  0.0900}
\DocumentationTok{\#\#  Avoidant {-} Fearful  {-}0.2188 0.1276 837  {-}1.714  0.3135}
\DocumentationTok{\#\# }
\DocumentationTok{\#\# Results are averaged over the levels of: gender }
\DocumentationTok{\#\# Results are given on the log (not the response) scale. }
\DocumentationTok{\#\# P value adjustment: mvt method for 6 tests}
\end{Highlighting}
\end{Shaded}

@@

To properly evaluate hypotheses with information regarding the expected direction of the effects, we use the Bayes factor with the encompassing prior approach. See the main article for a detailed introduction to this approach (\url{https://psyarxiv.com/6kc5u}).

@@

For each informative hypothesis, we obtain a hypothesis matrix that translates equality and inequality constraints according to the encompassing model parametrization. Formalization of informative hypotheses and the procedure to derive hypothesis matrices are described in the main paper (\url{https://psyarxiv.com/6kc5u}).

@@

\[
\pi_{adj}(\beta) \sim \mathcal{N}(0, \Sigma_{\beta}) = \mathcal{N}(0, R\Sigma_{\theta}R^T).
\]
Note that we set the mean vector to zero. The posterior is given by the same transformation
\[
Pr(\beta|Y) \sim \mathcal{N}(\hat{\beta}, \hat{\Sigma}_{\beta}) = \mathcal{N}(R\hat{\theta}-r, R\hat{\Sigma}_{\theta}R^T).
\]
For more details, see the main article available at \url{https://psyarxiv.com/6kc5u}.

@@

Before computing the Bayes factor, note that we have a set of comparable hypotheses as it exists a common solution to the set of linear equations obtained by setting all hypothesis constraints equal to zero. The solution is the trivial solution of simply considering all parameters equal to zero. Finally, we do not need to standardize our parameters as they represent mean groups' differences. For a detailed explanation, see the main article available at \url{https://psyarxiv.com/6kc5u}.

@@

To compute the Bayes factor we evaluate marginal densities and conditional probabilities as described in detail in the main article (\url{https://psyarxiv.com/6kc5u}). Bayes factor and posterior probability of each hypothesis are reported in Table\textasciitilde\ref{tab:table-bf-results-ext}.

@@

To interpret these patterns, remember that order constraints are insensitive to the distribution specification as long as the distribution is symmetric and centred on the constraint focal point. On the contrary, equality constraints are highly affected by the prior definition (for more details, see the main article available at \url{https://psyarxiv.com/6kc5u}).

@@

@@

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{emmeans}\SpecialCharTok{::}\FunctionTok{contrast}\NormalTok{(emmeans}\SpecialCharTok{::}\FunctionTok{emmeans}\NormalTok{(fit\_int\_mother, }\AttributeTok{specs =} \SpecialCharTok{\textasciitilde{}}\NormalTok{ mother ),}
                  \StringTok{"pairwise"}\NormalTok{, }\AttributeTok{adjust =} \StringTok{"mvt"}\NormalTok{)}
\DocumentationTok{\#\#  contrast           estimate     SE  df t.ratio p.value}
\DocumentationTok{\#\#  Secure {-} Anxious     {-}0.285 0.0892 837  {-}3.197  0.0075}
\DocumentationTok{\#\#  Secure {-} Avoidant    {-}0.120 0.0946 837  {-}1.266  0.5809}
\DocumentationTok{\#\#  Secure {-} Fearful     {-}0.469 0.1168 837  {-}4.011  0.0004}
\DocumentationTok{\#\#  Anxious {-} Avoidant    0.165 0.0869 837   1.903  0.2243}
\DocumentationTok{\#\#  Anxious {-} Fearful    {-}0.183 0.1096 837  {-}1.673  0.3346}
\DocumentationTok{\#\#  Avoidant {-} Fearful   {-}0.349 0.1167 837  {-}2.989  0.0152}
\DocumentationTok{\#\# }
\DocumentationTok{\#\# Results are averaged over the levels of: gender }
\DocumentationTok{\#\# Results are given on the log (not the response) scale. }
\DocumentationTok{\#\# P value adjustment: mvt method for 6 tests}
\end{Highlighting}
\end{Shaded}
